Calibrated, Parametrized Learning

### 2014-11-13 tex/parametrized-learning.tex
proof needed for N-P equivalence

Postulate:
\[
T' = \sum_{e=1}^n \underbrace{\log \left[ 1+c_1\frac {f_1(s(x_e) | \theta_0) }{ f_0(s(x_e) | \theta_0) } \right]}_{q(s_e)} \;,
\]
leads to an equivalent test, where $s_e \equiv s(x_e)$
\[
f_c(s) = \int dx \, \delta(s-s(x)) \, f_c(x)  \,  |\partial s / \partial x|^{-1}
\]

@@

Proof:

First show $q(x_e) = q(s(x_e))$.
\[
\frac {f_1(s(x) | \theta_0) }{ f_0(s(x) | \theta_0) } = \frac { \int dx \delta(s-s(x)) \, f_1(x_e | \theta_0) J }{ \int dx \delta(s-s(x)) \, f_0(x_e | \theta_0) J } = \frac {f_1(x | \theta_0) }{ f_0(x | \theta_0) } 
\]

Second, show density is the same

@@

\[
f_c(q_s) = \int dx \delta(q_s-q_s(s(x))) \, f_c(x) \, / |\partial q_s / \partial x|
\]

@@

>>>>

\textbf{Postulate:}
\[
T' = \sum_{e=1}^n \underbrace{\log \left[ 1+c_1\frac {f_1(s(x_e) | \theta_0) }{ f_0(s(x_e) | \theta_0) } \right]}_{q(s_e)} \;,
\]
leads to an equivalent test, where $s_e \equiv s(x_e)$
\[
f_c(s) = \int dx \, \delta(s-s(x)) \, f_c(x)  \,  |\partial s / \partial x|^{-1}
\]

@@

\textbf{Proof (in progress):}

We want to show density is the same

@@

\[
f_c(q_s) = \int dx \delta(q_s-q_s(s(x))) \, f_c(x) \, / |\partial q_s / \partial x|
\]
sufficient to show $q(x_e) = q(s(x_e))$.  Here we use that $f_1(x)/f_0(x)=\textrm{const}$ for all points on the level-set $\Omega_c$ given by $ \delta(c-s(x))$. 
\[
\frac {f_1(c | \theta_0) }{ f_0(c | \theta_0) } = 
\frac { \int dx \delta(c-s(x)) \, f_1(x_e | \theta_0) }{ \int dx \delta(c-s(x)) \, f_0(x | \theta_0)  } = 
\frac {c \int dx \delta(c-s(x)) \, f_0(x | \theta_0)  }{ \int dx \delta(s-s(x)) \, f_0(x | \theta_0)  } = c =\frac {f_1(x | \theta_0) }{ f_0(x | \theta_0) } 
\]

@@

\newpage

Given $x\in \mathbb{R}^n$ and two smooth, real-valued functions $f_1(x)$ and $f_0(x)$ define 
\[ 
s(x)=\frac{f_1(x)}{f_2(x)}
\].
Define $g_1(c) = \int dx \delta(c - s(x) ) \, f_1(x)$ and $g_0(c) = \int dx \delta(c - s(x) ) \, f_0(x)$.
I wish to show
\[
\frac{g_1(c)}{g_0(c)} = \frac{f_1(x)}{f_0(x)}
\]
$\forall x \ni s(x)=c$.

Sketch of Proof: 
let $\Omega_{c}$ be the level set $\{x \mid s(x) = c \}$ and $\hat{n}=\nabla s(x) / |\nabla s(x)|$ be the perpendicular direction to the surface at the point $x$. The  coordinate perpendicular to $\Omega$ can be written $y = x+\epsilon \hat{n}$. In these coordinates, the integral $\int dx \to \int d\Omega d\epsilon$, thus
\[
g_1(c) = \int dx \delta(c-s(x)) f_1(x) = \int d\Omega f_1(x) / |\partial s(x)/\partial \epsilon|
\]
Similarly for $g_0(c)$. We can factor out of the integral $s(x)=f_1(x)/f_0(x)$ since it is constant over $\Omega$.
Thus
\[
g_1(c) = \int dx \delta(c-s(x)) f_1(x) = \int d\Omega f_1(x) / |\partial s(x)/\partial \epsilon| = s(x) \int d\Omega f_0(x) / |\partial s(x)/\partial \epsilon|
\]
and we arrive at the result
\[
\frac{g_1(c)}{g_0(c)} = \frac{s(x) \int d\Omega f_0(x) / |\partial s(x)/\partial \epsilon|}{ \int d\Omega f_0(x) / |\partial s(x)/\partial \epsilon|} = \frac{f_1(x)}{f_0(x)} \;.
\]

\newpage
